Tidal field anisotropy as a tracer of cosmic voids

### 2015-02-13 cosmic_voids.tex
redistribuyendo graficas, revisando la parte de density profile

  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{delta_L1.pdf}  
  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.3\textheight]{FA_L1.pdf}

@@

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.3\textheight]{voids_regions_volume_all.pdf}

@@

Void shapes exhibit a wide range of geometries.
To define their size we use its equivalent spherical radius or
effective radius, defined as $\reff = [3/(4\pi)V]^{1/3}$, with $V$ the 
total volume of the void. 
In Figure \ref{fig:volume_function} we show the void size
distributions for the T-Web and the V-Web.

We see that the void distribution for the T-Web is broadly consistent with the
expectations from a two-barrier problem  \citep{Sheth04}. 
The formation of large voids is limited by the \textit{void-in-void}
problem (first barrier), where large voids are constituted
hierarchically of smaller ones. 
In turn, the formation of small  voids is damped by the
\textit{void-in-cloud} problem (second barrier),  where nearby
collapsing structures limit the abundance of embedded small  voids.

We also find that the V-Web scheme produces an over-abundance of small
voids compared to the resuls of the T-Web.
A large number of these small voids are embedded in dense regions. 
They are visible in the middle panel of Figure \ref{fig:FA_field} as
the small bubbles located inside sheets.
The existence of these small voids could be qualitatively explained by
dynamics of shell crossing in collapsing sheets. 
When matter colides into a sheet, at their center it is possible to
find crossing matter planes that effectively give a possitively
divergen velocity field, which gives a void identification by the
T-Web algorithm. This points has been discussed in \citet{Hoffman12}.

Comparing the abundance of large voids in the two web schemes, we find
that the V-Web is limited to have voids on the scale of $\sim 10$\hMpc,
while the T-Web scheme includes voids as large as $\sim 15$\hMpc. 
Large voids in the T-Web scheme have a velocity structure that
induces a split by the watersched algorithm in the V-Web. 
This is eviden in the right panel of Figure \ref{fig:FA_field}.

%-------------------------------------------------------------------------
\subsection{Compenseated and overcompensated voids}
\label{subsec:enclosedmass}
%-------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------
\subsection{Physical profiles of voids}
\label{subsec:properties_voids}
%-------------------------------------------------------------------------

%.........................................................................
%FIGURE 4: Density profile of voids for each defined scheme
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_FA_TwebFAG0.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_density_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_velocity_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_FA_VwebFAG0.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_density_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_velocity_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_FA_TwebFAG1.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_density_VwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_velocity_VwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{voids_FA_VwebFAG1.pdf}

In Fig. \ref{fig:RhoVel} we analyse the internal properties of the found 
voids. We calculate the contrast density, radial-projected velocity and 
FA profiles. For this purpose we catalogue all the voids in several radial 
bins in order to capture possible size effects; moreover we show profiles 
for both, subcompensated and overcompensated voids. Then, for each void, 
we take the distance of each member cell to the void centre along with the 
properties of interest. Normalizing these distances with the effective 
radius, we stack all the voids of a radial bin in order to compute the 
radial profiles.

%.........................................................................
\subsubsection{Density profiles}
\label{subsubsec:density_voids}
%.........................................................................

In left panels of Fig. \ref{fig:RhoVel} we compute density profiles of 
voids stacked according to their size and their compensation index. 
Instead of calculating the radial internal structure inside the effective
radius, we opted for a radius well beyond that value ($8\ \reff$) in order 
to capture the properties of neighbour structures as well.

A first interesting result is the value at the void centres: the larger the 
void, the more underdense their value at the centre, ranging from $\delta
\approx-0.95$ for the largest voids ($8.3-12\ \hMpc$) to $\delta\approx 
-0.8$ for the smallest voids ($2-3.2\ \hMpc$). This holds for all the voids 
in both schemes. These very low values are consistent with most of the void 
finding schemes based on smooth and continuous fields from simulation or 
reconstruction procedures on surveys \citep{Plionis02, Colberg05, Shandarin06, 
Platen07, Neyrinck08, MunozCuartas11, Neyrinck13, Ricciardelli2013}, unlike
geometrical approaches based on point distributions, where central values
are generally higher \citep{Colberg08}.

>>>>

  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{delta_L1.pdf}  
  \includegraphics[trim = 2mm 2mm 5mm 10mm, clip, keepaspectratio=true,
  width=0.35\textheight]{FA_L1.pdf}

@@

  \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, keepaspectratio=true,
  width=0.35\textheight]{voids_regions_volume_all.pdf}

@@

Void shapes exhibit a wide range of geometries.
To define their size we use its equivalent spherical radius or
effective radius, defined as $\reff = [3/(4\pi)V]^{1/3}$, with $V$ the 
total volume of the void computed from the individual grid cells
assigned to the void.   
In Figure \ref{fig:volume_function} we show the void size
distributions for the T-Web and the V-Web.

We see that the void distribution for the T-Web is broadly consistent with the
expectations from a two-barrier problem  \citep{Sheth04}. 
The formation of large voids is limited by the \textit{void-in-void}
problem (first barrier), where large voids are constituted
hierarchically of smaller ones. 
In turn, the formation of small voids is damped by the
\textit{void-in-cloud} problem (second barrier),  where nearby
collapsing structures limit the abundance of small embedded voids.

We also find that the V-Web scheme produces an over-abundance of small
voids compared to the resuls of the T-Web.
A large number of these small voids are embedded in overdense regions. 
They are visible in the middle panel of Figure \ref{fig:FA_field} as
small bubbles located inside sheets.
The existence of these small voids can be explained by
dynamics of shell crossing in collapsing sheets. 
As matter colides into a sheet, in their symmetry plane one will
find crossing ahseets that effectively give a positive divergence in
the velocity field, resulting in a void identification by the
V-Web algorithm. This points has been discussed in \citet{Hoffman12}.

Comparing the abundance of large voids in the two web schemes, we find
that the V-Web is limited to have voids on the scale of $\sim 10$\hMpc,
while the T-Web scheme includes voids as large as $\sim 15$\hMpc. 
Large voids in the T-Web scheme have a velocity structure that
induces a split by the watershed algorithm in the V-Web. 
This is evident in the right panel of Figure \ref{fig:FA_field}.

%.........................................................................
%FIGURE 4: Density profile of voids for each defined scheme
\begin{figure*}
\centering
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_density_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_density_TwebFAG1.pdf}

  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_density_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_density_VwebFAG1.pdf}

  \captionof{figure}{\small Physical internal properties of voids for 
  the two finding scheme. Density field (left panels), radial-projected
  velocity field (middle panels) and FA field (right panels). The analysis
  is performed for both, subcompensated (first two rows) and overcompensated
  voids (last two rows).}
  \label{fig:RhoVel}
  \vspace{0.1 cm}
\end{figure*}

\begin{figure*}
\centering  
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_velocity_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_velocity_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_velocity_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_velocity_VwebFAG1.pdf}
  \captionof{figure}{\small Physical internal properties of voids for 
  the two finding scheme. Density field (left panels), radial-projected
  velocity field (middle panels) and FA field (right panels). The analysis
  is performed for both, subcompensated (first two rows) and overcompensated
  voids (last two rows).}

\end{figure*}

\begin{figure*}
\centering  
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_FA_TwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_FA_VwebFAG0.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_FA_TwebFAG1.pdf}
  \includegraphics[trim = 1mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.32\textheight]{voids_FA_VwebFAG1.pdf}

%-------------------------------------------------------------------------
\subsection{Subcompensated and overcompensated voids}
\label{subsec:enclosedmass}
%-------------------------------------------------------------------------

@@

In Figure \ref{fig:RhoVel} we show the density and velocity profiles
of voids splitted in these two families. 
In the left column it becomes clear the difference between sub- and
overcompensated voids.

%.........................................................................
\subsection{Density profiles}
\label{subsec:density_voids}
%.........................................................................

We calculate the contrast density, radial-projected velocity and 
FA profiles. For this purpose we catalogue all the voids in several radial 
bins in order to capture possible size effects; moreover we show profiles 
for both, subcompensated and overcompensated voids. Then, for each void, 
we take the distance of each member cell to the void centre along with the 
properties of interest. Normalizing these distances with the effective 
radius, we stack all the voids of a radial bin in order to compute the 
radial profiles.

The left column in Figure \ref{fig:RhoVel} shows the results of
stacked density profiles for different void sizes. 
We normalize the radial coordinate with the effective radius to check
for possible universal features among voids. 
We calculate the profile out to a radius $8\ \reff$  to capture the
the point where the overdensity reaches the mean value.

A first interesting result is the overdensity value at the void's
center.
We find that larger voids have a lower overdensity value.
The largest voids ($8.3-12\ \hMpc$) have an underdensity
$\approx-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\approx 
-0.8$ at their centers.
This holds for both web schemes.

These values are consistent with most of the void finding schemes
based on smooth and continuous fields from simulation or
reconstruction procedures on surveys \citep{Plionis02, Colberg05,
  Shandarin06,  Platen07, Neyrinck08, MunozCuartas11, Neyrinck13,
  Ricciardelli2013}, unlike geometrical approaches based on point
distributions, where central density values are generally higher
\citep{Colberg08}.
